Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
fixed proof for prop4.
Applications take up space, never mind
No todos left
more fixes to proof4.
restatable props.

@@

\theoremstyle{definition}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{example}{Example}

@@

% Maths operators
\newcommand{\paths}{\operatorname{paths}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
\newcommand{\V}{\operatorname{V}}
\newcommand{\N}{\operatorname{N}}
\newcommand{\nds}{\operatorname{S}}
\newcommand{\loopcomp}[1]{\oset[.1ex]{\multimap}{#1}}
% to do comments
\usepackage{color}
\newcommand{\todo}[1]{{\color{red} {?? [}{#1}{]}}}

@@

\section{Introduction}
\todo{talk about subgraph isomorphism applications, particularly vision}

@@

\begin{figure}
    \begin{center}
        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm,node distance=10mm,fill=black}]
            \node[fill=uofgcobalt] (a) {};
            \node (a1) [below left of = a] {};
            \node (b1) [below right of = a] {};
            \node (aa) [below right of = a1] {};

@@

\begin{proposition}\label{prop:comp}
Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P
\hookrightarrow T$ if and only if $i$ satisfies both the definition of $P \rightarrowtail T$ and
of $\loopcomp{P} \rightarrowtail \loopcomp{T}$.
Similarly, $i$ satisfies the definition of $P
\lessind{k} T$ if and only if $i$ satisfies both the definition of $P \lessnonind{k} T$ and of
$\loopcomp{P}
\lessnonind{k} \loopcomp{T}$.
\end{proposition}

@@

\begin{proposition}
    \label{prop:deg}
    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
    $k$-less-subgraph isomorphisms, if $p \lessmap{k} t$ then
    $\deg(p) - k \le \deg(t)$.
\end{proposition}

@@

\begin{proposition}\label{prop:nds}
If $p \lessmap{k} t$, then $\nds(p) \lesspreceq{k} \nds(t)$.
\end{proposition}

@@

\begin{proposition}\label{prop:paths}
    Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
     $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
\end{proposition}

@@

\section{Proofs Omitted From Main Text}

\begin{proof}[Proof of \cref{prop:deg}]
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t). \qedhere
\]
\end{proof}

\begin{proof}[Proof of \cref{prop:nds}]
Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
implies that $\left|\nds(p)\right| -k \leq \left| \nds(t) \right| $.

@@

\begin{proof}[Proof of \cref{prop:paths}]
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
$P_{2} = \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \}$. As we are looking at paths of length 2, the
intermediate vertices lie in both neigbour vertex sets of $p$ and $q$. We can rewrite $P_{2}$ as
$P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}$, in other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and $q$,
$P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \}$. So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.

If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
\[
\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
\]
As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
\[
\left|\N(p)\cap \N(q)\right| - k \leq \deg(p) - k\leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)
\]
which is
\[
\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
\]
\end{proof}

>>>>

% to restate the propostions
\usepackage{thmtools,thm-restate}

\declaretheorem[name=Proposition,style=definition]{proposition}

@@

\theoremstyle{definition}
\newtheorem{corollary}{Corollary}
\newtheorem{example}{Example}

@@

% Maths operators
\newcommand{\paths}{\operatorname{paths}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
\newcommand{\V}{\operatorname{V}}
\newcommand{\N}{\operatorname{N}}
\newcommand{\nds}{\operatorname{S}}
\newcommand{\loopcomp}[1]{\oset[.1ex]{\multimap}{#1}}

@@

\section{Introduction}

@@

\begin{figure}
    \begin{center}
        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm,node
            distance=10mm,fill=black}, scale=0.2]
            \node[fill=uofgcobalt] (a) {};
            \node (a1) [below left of = a] {};
            \node (b1) [below right of = a] {};
            \node (aa) [below right of = a1] {};

@@

\begin{proposition}
    \label{prop:comp}
Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P
\hookrightarrow T$ if and only if $i$ satisfies both the definition of $P \rightarrowtail T$ and
of $\loopcomp{P} \rightarrowtail \loopcomp{T}$.
Similarly, $i$ satisfies the definition of $P
\lessind{k} T$ if and only if $i$ satisfies both the definition of $P \lessnonind{k} T$ and of
$\loopcomp{P}
\lessnonind{k} \loopcomp{T}$.
\end{proposition}

@@

\begin{restatable}{proposition}{propdeg}\label{prop:deg}
    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
    $k$-less-subgraph isomorphisms, if $p \lessmap{k} t$ then
    $\deg(p) - k \le \deg(t)$.
\end{restatable}

@@

\begin{restatable}{proposition}{propnds}\label{prop:nds}
If $p \lessmap{k} t$, then $\nds(p) \lesspreceq{k} \nds(t)$.
\end{restatable}

@@

\begin{restatable}{proposition}{proppaths}\label{prop:paths}
    Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
     $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
\end{restatable}

@@

\section{Proofs Omitted From Main Text}
\propdeg*
\begin{proof}
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t). \qedhere
\]
\end{proof}

\propnds*
\begin{proof}
Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
implies that $\left|\nds(p)\right| -k \leq \left| \nds(t) \right| $.

@@

\proppaths*
\begin{proof}
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
$P_{2} = \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \}$. As we are looking at paths of length 2, the
intermediate vertices lie in both neigbour vertex sets of $p$ and $q$. We can rewrite $P_{2}$ as
$P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}$, in other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and $q$,
$P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \}$. So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.

If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
\[
\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
\]
As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
\begin{align*}
\left|\N(p)\cap \N(q)\right| - k & \leq \deg(p) - k \\
 & \leq \left|\N(t)\cap \N(u)\right|\\
 & \leq \deg(t)
\end{align*}
which is
\[
\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
\]
\end{proof}
